The stakeholders are the individuals or groups who are relevant 
to the issues of this project.
There are three main stakeholders in this project:
\begin{itemize}
    \item User
    \item Developer
    \item Project Owner
\end{itemize}

\paragraph{User} 
% The user is the person who will use the system. 
% In this project, we can easily identify the user is the customer 
% who will use the web application to manage their device and users,
% and create the RAI and Tunnel.

% The user in this project are require the web application 
% should be oprate easily, the features in this web application 
% can be recongnized easily and the usage should be obivously.

The user is the person who will use the system. 
In this project, the user refers to the customer 
who will utilize the web application 
to manage their devices, users, and create the RAI and Tunnel.

The user's requirements for the web application 
include ease of operation, 
intuitive recognition of features, 
and clear usability.

\paragraph{Project Owner}
% The project owner is the person who will manage the project, 
% in this case, 
% the project owner is the company who own the product. 

% The project owner is require the project should be finished in time, 
% can be coporeate 
% with the hardware which be developed by the company,
% and the project can be easily to maintain, update, magration, 
% and handover to other developers.

The project owner is the individual or organization responsible for managing the project. In this case, the project owner is the company that owns the product.

The project owner has several requirements for the project:

\begin{itemize}
    \item Timely completion of the project.
    \item Compatibility with the hardware developed by the company.
    \item Easy maintenance, updates, migration, and handover to other developers.
\end{itemize}

\paragraph{Developer}
% The developer is the person who will develop, modify, 
% scale and fix the system in any situation.

% Therefore, the entire system should be easy to understand 
% with the comments, 
% easy to modify with the clear structure, 
% easy to scale with reusable compoents 
% and easy to identify the issue to fix any bugs.

The developer is responsible for developing, modifying, 
scaling, and fixing the system in any situation.

To facilitate these tasks, the system should have clear 
and concise comments,
a well-organized structure that is easy 
to modify, reusable components for easy scalability, 
and effective bug identification for efficient issue resolution.

