\paragraph{Git}
Git is a distributed version-control system for tracking changes in source code during software development.
It is designed for coordinating work among programmers, but it can be used to track changes in any set of files.
Its goals include speed, data integrity, and support for distributed, non-linear workflows.

\paragraph{GitHub}
GitHub is a provider of Internet hosting for software development and version control using Git.
It offers the distributed version control and source code management (SCM) functionality of Git,
plus its own features.
It provides access control and several collaboration features such as bug tracking, feature requests, task management, and wikis for every project.

\paragraph{GitHub Actions}
GitHub Actions is an API for cause and effect on GitHub: orchestrate any workflow, based on any event, 
while GitHub manages the execution, provides rich feedback, and secures every step along the way.
With GitHub Actions, workflows and steps are just code in a repository, so you can create, share, reuse, and fork your software development practices.

\paragraph{Docker}
Docker is a set of platform as a service (PaaS) products that use OS-level virtualization to deliver software in packages called containers.
Containers are isolated from one another and bundle their own software, libraries and configuration files;
they can communicate with each other through well-defined channels.
All containers are run by a single operating system kernel and are thus more lightweight than virtual machines.
Containers are created from images that specify their precise contents.
Images are often created by combining and modifying standard images downloaded from public repositories.
