\paragraph{JAVASCRIPTl}
JavaScript is the most popular language for the front-end development. 


\paragraph{React} 
is a JavaScript library for building user interfaces. 
It is maintained by Facebook and a community of individual developers and companies.
React can be used as a base in the development of single-page or mobile applications.
However, React is only concerned with state management and rendering that state to the DOM,
so creating React applications usually requires the use of additional libraries for routing,
as well as certain client-side functionality.
React Router is an example of such a library.


\paragraph{React-Router} is a routing library for React.
It abstracts away the details of server and client and allows developers to focus on building apps.
It offers a simple, declarative API to let you build URL (Uniform Resource Locator) routing with ease.
It supports server-side rendering and comes with routers for browsers and Node.js.


\paragraph{Redux} is a predictable state container for JavaScript apps.
It helps you write applications that behave consistently, run in different environments (client, server, and native),
and are easy to test.
On top of that, it provides a great developer experience, such as live code editing combined with a time traveling debugger.


\paragraph{RTK} is a powerful, opinionated Redux toolset for writing better reducers,
organizing and accessing state in components, and managing side effects.
It was originally created to help address three common concerns about Redux:


\paragraph{RTKQ} is a powerful data fetching and caching tool.
It is designed to simplify common cases for loading data in a web application, 
eliminating the need to hand-write data fetching \& caching logic yourself.


\paragraph{TailwindCSS} is a utility-first CSS framework for rapidly building custom user interfaces.
It is a highly customizable, low-level CSS framework that gives you all of the building blocks you need to build bespoke designs without any annoying opinionated styles you have to fight to override.


\paragraph{Semantic UI} is a development framework that helps create beautiful, responsive layouts using human-friendly HTML.
Semantic UI treats words and classes as exchangeable concepts.
Classes use syntax from natural languages like noun/modifier relationships, word order, and plurality to link concepts intuitively.


\paragraph{Jest} is a JavaScript testing framework maintained by Facebook, Inc.
designed and built by Christoph Nakazawa with a focus on simplicity and support for large web applications.
It works with projects using Babel, TypeScript, Node.js, React, Angular, Vue.js and Svelte.
Jest does not require a browser to run tests, and it runs tests in parallel - this makes Jest fast.
Jest is well-documented, requires little configuration and can be extended to match your requirements.
