The Agile software development is a set of software development methods
to aim to provide a sustainable, iterative and incremental software development
process.

The Agile promotes adaptive planning, evolutionary development, early delivery,
continuous improvement, encourages rapid and flexible response to change.

Since this project is a single person project, the Agile software development
method is not suitable for this project. However, the Agile software development
method is still a good reference for the project management.

Therefore, in this project will try to use part of the scrum method to manage
the project daily tasks.

The fully period of this project from 10/15/2023 to 1/15/2024, which will cost 
three months. The project will be divided into six sprints, each sprint will
be contained two weeks. The first sprint will be started 
from 10/15/2023 to 10/29/2023,
and the last sprint will be started from 12/31/2023 to 1/15/2024. 

The first sprint will be used to do the requirement analysis, the domain model
analysis, the Technology research.

The second sprint will be used to do the system design, which included the 
database design, the back-end design, the front-end design, and the DevOps 
design.

The third sprint will be used to do the overall development, to make the entire
system can be run without any useful features.

The fourth sprint will be used to do the feature development, to implement the
basic functionalities of the system.

The fifth sprint will be used to do the connection development, which use for 
creating a session from the local device to the remote equipment.

The last sprint will be used to do the testing, the deployment, and the
documentation.